### 2017-04-04 paper/evaluation.tex
pass on text

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        medium & Javaslang & 3 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with test execution in parallel enabled by
    default}
    \label{tab:freqmodes-dynamic}
\end{figure}

\subsubsection{Support of parallelization configuration in build files}
\label{sec:rqC-2}

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
To reduce the number of build files
to inspect, we consider only \pomf{} files that contain
\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
node. Figure~\ref{fig:surefire-configuration} shows an example of
configuration node mined. This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.

Finally, some projects use a value informed as an argument in the
command line instead of declaring a static value in the configuration
file (\ie, \pomf{}). In this case, we consider all valid values for
the parameter.

@@

Figure~\ref{tab:inspection-table} summarizes our results. The first
column indicates the group of projects according to their time cost.
The second column indicates the number of build files per group. 
The last column indicates the ratio of projects with parallelization settings.

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
The \numPomMatched{} configurations are distributed across \numProjectsPar{} projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
        \toprule
        \multirow{2}{*}{Group} %1st row, 1st cell
            & \multirow{2}{*}{\# \pomf{}}
	    & \# \pomf{} matched\\
        % 2nd row - empty cell
            & % empty cell
            & / total\\%
        \midrule%
	Long   & \numPomLong{} & 4 / \numLong{}\\%
	Medium & \numPomMed{} & 6 / \numMed{}\\%
        \midrule%
        Total % last row, first cell
            & \pomMedLong{}
            & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
identified above, we investigated further the \numPomMatched{}
build files with parallel settings.  We analyzed the support and
distribution of parallel modes from this subset of projects. To
calculate the distribution of parallel modes, we considered only the
presence of the mode in at least one of the project settings.  Recall
that a build file may contain more than one parallel setting and a
project may contain several sub-modules with build files.  In case the
value of a parallel option is resolved dynamically (\eg, via
command-line argument or system variable) we compute all modes related
to the option. For instance, depending on the value, the
\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings.
\Fix{Missing conclusion: Fork the most used configuration}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
    identified statically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode.}
\end{figure}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused by defailt given that only
	  \percentParallel{}
      of projects supports parallel execution of test suites without
	  any extra parameter.}
  \end{minipage}
}
\end{center}

>>>>

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}

To extend our previous investigation, we evaluated the presence of
parallelism configuration in several build files (\ie, \pomf{} files)
from the same sample set of \numMedLong{} projects. The rationale is
that some projects may have support to parallel execution but it is
deactivated by default (\ie, require additional arguments before the
test execution). For instance, on Maven, it is possible to create
multiple configurations in the same build file and activate any of
them dynamically.  To reduce the space of \Fix{x} build files, we
considered a subset of \Fix{y} build files with the following
criteria: the given \pomf{} file has \CodeIn{maven-surefire-plugin}
plugin declaration and it has an explicit \CodeIn{configuration}
declaration. We automatically parsed these \Fix{y} files and we used
the same approach to classify the parallelization mode from the parsed
configurations as in our previous analysis. In an initial analysis, we
noticed that some projects do not declare a static value in some
parameters, instead, these projects inform the actual value in the
command line. To handle this case, we computed all valid values for
the parameter.

@@

Figure~\ref{tab:inspection-table} summarizes our results. \Fix{The first
column indicates the group of projects according to their time cost.
The second column indicates the number of build files per group.
The last column indicates the ratio of projects with parallelization settings.
From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
The \numPomMatched{} configurations are distributed across
\numProjectsPar{} projects from our sample.}

% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{\Fix{This is a COPY from the previous table!}}
    \label{tab:inspection-table}
\end{figure}

%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused by default given that
      only \percentParallel{} of projects  (5 out of \numMedLong)
      supports parallel execution of test suites without any extra
      parameter.}
  \end{minipage}
}
\end{center}
